---
title: "rsconnect"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Package ‘rsconnect’
January 10, 2019
Type Package
Title Deployment Interface for R Markdown Documents and Shiny
Applications
Version 0.8.13
Author JJ Allaire
Maintainer Jonathan McPherson <jonathan@rstudio.com>

#### Description
 Programmatic deployment interface for 'RPubs', 'shinyapps.io', and
'RStudio Connect'. Supported content types include R Markdown documents,
Shiny applications, Plumber APIs, plots, and static web content.
Depends R (>= 3.0.0)
Imports openssl, RCurl, jsonlite, packrat (>= 0.4.8-1), yaml (>=
2.1.5), rstudioapi (>= 0.5)
Suggests knitr, testthat, rmarkdown (>= 1.1), plumber (>= 0.3.2),
reticulate, shiny, sourcetools, xtable
License GPL-2
RoxygenNote 6.1.1
NeedsCompilation no
Repository CRAN
Date/Publication 2019-01-10 19:50:03 UTC
R topics documented:
rsconnect-package .
accounts . . . . . .
account
#### Usage
<pre><code>
 . . .
addAuthorizedUser
addLinter . . . . .
appDependencies .
applications . . . .
authorizedUsers . .
configureApp . . .
.
.
.
.
1
.
2
3
4
5
5
6
8
9
92
rsconnect-package
connectUser . . . . . .
deployAPI . . . . . . .
deployApp . . . . . . .
deployDoc . . . . . . .
deployments . . . . . .
deploySite . . . . . . .
deployTFModel . . . .
forgetDeployment . . .
generateAppName . .
lint . . . . . . . . . . .
linter . . . . . . . . . .
listBundleFiles . . . .
makeLinterMessage . .
removeAuthorizedUser
restartApp . . . . . . .
rpubsUpload . . . . . .
rsconnectOptions . . .
rsconnectPackages . .
servers . . . . . . . . .
setAccountInfo . . . .
setProperty . . . . . .
showInvited . . . . . .
showLogs . . . . . . .
showMetrics . . . . . .
showProperties . . . .
show
#### Usage
<pre><code>
 . . . . . .
showUsers . . . . . . .
taskLog . . . . . . . .
tasks . . . . . . . . . .
terminateApp . . . . .
unsetProperty . . . . .
writeManifest . . . . .
.
.


Deployment Interface for R Markdown Documents and Shiny Appli-
cations

#### Description

The ‘rsconnect“ package provides a programmatic deployment interface for RPubs, shinyapps.io,
and RStudio Connect. Supported contents types include R Markdown documents, Shiny applica-
tions, plots, and static web content.accounts
3
Managing Applications
Deploy and manage applications with the following functions:
•
•
•
•
•
deployApp(): Deploy a Shiny application to a server.
configureApp(): Configure an application currently running on a server.
restartApp(): Restart an application currently running on a server.
terminateApp(): Terminate an application currently running on a server.
deployments(): List deployment records for a given application directory.
More information on application management is available in the applications() help page.
Managing Accounts and Users
Manage accounts on the local system.
• setAccountInfo(): Register an account.
• removeAccount(): Remove an account.
• accountInfo(): View information for a given account.
More information on account management is available in the accounts() help page.
accounts
Account Management Functions

#### Description

Functions to enumerate and remove accounts on the local system. Prior to deploying applications
you need to register your account on the local system.

#### Usage
<pre><code>

accounts(server = NULL)
accountInfo(name, server = NULL)
removeAccount(name, server = NULL)

</code></pre>
#### Arguments

server
name
Name of the server on which the account is registered (optional; see servers())
Name of account

#### Details
You register an account using the setAccountInfo() function (for ShinyApps) or connectUser()
function (for other servers). You can subsequently remove the account using the removeAccount
function.
The accounts and accountInfo functions are provided for viewing previously registered accounts.4
account
#### Usage
<pre><code>

Value
accounts returns a data frame with the names of all accounts registered on the system and the
servers on which they reside. accountInfo returns a list with account details.
See Also
Other Account functions: connectUser, setAccountInfo
account
#### Usage
<pre><code>

Show Account 
#### Usage
<pre><code>


#### Description

Show account usage

#### Usage
<pre><code>

account
#### Usage
<pre><code>
(account = NULL, server = NULL, usageType = "hours",
from = NULL, until = NULL, interval = NULL)

</code></pre>
#### Arguments

account Account name. If a single account is registered on the system then this parameter
can be omitted.
server Server name. Required only if you use the same account name on multiple
servers.
usageType Use metric to retreive (for example: "hours")
from Date range starting timestamp (Unix timestamp or relative time delta such as
"2d" or "3w").
until Date range ending timestamp (Unix timestamp or relative time delta such as
"2d" or "3w").
interval Summarization interval. Data points at intervals less then this will be grouped.
(Number of seconds or relative time delta e.g. "1h").
Note
This function only works for ShinyApps servers.


## addAuthorizedUser

Add authorized user to application

#### Description

Add authorized user to application

#### Usage
<pre><code>

addAuthorizedUser(email, appDir = getwd(), appName = NULL,
account = NULL, server = NULL, sendEmail = NULL,
emailMessage = NULL)

</code></pre>
#### Arguments

* ``email``: Email address of user to add.
* ``appDir``: Directory containing application. Defaults to current working directory.
* ``appName``: Name of application.
* ``account``: Account name. If a single account is registered on the system then this parameter
can be omitted.
* ``server``: Server name. Required only if you use the same account name on multiple servers.
* ``sendEmail``: Send an email letting the user know the application has been shared with them.
* ``emailMessage``: Optional character vector of length 1 containing a custom message to send in email invitation. Defaults to NULL, which will use default invitation message.

#### Note
This function works only for ShinyApps servers.

#### See Also
removeAuthorizedUser() and showUsers()



8
applications

authorizedUsers
(Deprecated) List authorized users for an application

#### Description

(Deprecated) List authorized users for an application

#### Usage
<pre><code>

authorizedUsers(appDir = getwd())

</code></pre>
#### Arguments

appDir




connectUser
Connect User Account

#### Description

Connect a user account to the package so that it can be used to deploy and manage applications on
behalf of the account.

#### Usage
<pre><code>

connectUser(account = NULL, server = NULL, quiet = FALSE)

</code></pre>
#### Arguments

* ``account``:   A name for the account to connect. Optional.
server The server to connect to. Optional if there is only one server registered.
quiet Whether or not to show messages and prompts while connecting the account.
Details
When this function is invoked, a web browser will be opened to a page on the target server where you
will be prompted to enter your credentials. Upon successful authentication, your local installation
of rsconnect and your server account will be paired, and you’ll be able to deploy and manage
applications using the package without further prompts for credentials.
See Also
Other Account functions: accounts, setAccountInfo


deployDoc
Deploy a Document

#### Description

Deploys an application consisting of a single R Markdown document or other single file (such as
an HTML or PDF document).

#### Usage
<pre><code>

deployDoc(doc, ...)14
deployments

</code></pre>
#### Arguments

doc
...
Path to the document to deploy.
Additional arguments to deployApp(). Do not supply appDir, appFiles, or
appPrimaryDoc; these three parameters are automatically generated by deployDoc
from the document.
Details
When deploying an R Markdown document, any files which are required to render and display the
file must be deployed.
This method discovers these additional files using rmarkdown::find_external_resources() from
rmarkdown.
If you find that the document is missing dependencies, either specify the dependencies explicitly in
the document (the documentation for rmarkdown::find_external_resources() explains how to
do this), or call deployApp() directly and specify your own file list in the appFiles parameter.
See Also
Other Deployment functions: applications, deployAPI, deployApp, deploySite, deployTFModel
deployments
List Application Deployments

#### Description

List deployment records for a given application.

#### Usage
<pre><code>

deployments(appPath, nameFilter = NULL, accountFilter = NULL,
serverFilter = NULL, excludeOrphaned = TRUE)

</code></pre>
#### Arguments

appPath
nameFilter
accountFilter
serverFilter
excludeOrphaned
The path to the content that was deployed, either a directory or an individual
document.
Return only deployments matching the given name (optional)
Return only deployments matching the given account (optional)
Return only deployments matching the given server (optional)
If TRUE (the default), return only deployments made by a currently registered
account. Deployments made from accounts that are no longer registered (via
e.g.removeAccount()) will not be returned.
Value
Returns a data frame with at least following columns:deploySite
15
name
account
bundleId
url
when
Name of deployed application
Account owning deployed application
Identifier of deployed application’s bundle
URL of deployed application
When the application was deployed (in seconds since the epoch)
If additional metadata has been saved with the deployment record using the metadata argument to
deployApp(), the frame will include additional columns.
See Also
applications() to get a list of deployments from the server, and deployApp() to create a new
deployment.

#### Examples
```{r}

## Not run:
# Return all deployments of the ~/r/myapp directory made with the 'abc'
# account
deployments("~/r/myapp", accountFilter="abc")
## End(Not run)
```

deploySite
Deploy a Website

#### Description

Deploy an R Markdown website to a server.

#### Usage
<pre><code>

deploySite(siteDir = getwd(), siteName = NULL, account = NULL,
server = NULL, render = c("none", "local", "server"),
launch.browser = getOption("rsconnect.launch.browser", interactive()),
logLevel = c("normal", "quiet", "verbose"), lint = FALSE,
metadata = list(), python = NULL)

</code></pre>
#### Arguments

siteDir Directory containing website. Defaults to current working directory.
siteName Name for the site (names must be unique within an account). Defaults to the
base name of the specified siteDir, (or to a name provided by a custom site
generation function).16
deployTFModel
account Account to deploy application to. This parameter is only required for the initial
deployment of an application when there are multiple accounts configured on
the system (see accounts).
server Server name. Required only if you use the same account name on multiple
servers.
render Rendering behavior for site: "none" to upload a static version of the current
contents of the site directory; "local" to render the site locally then upload it;
"server" to render the site on the server. Note that for "none" and "local" R
scripts (.R) and markdown documents (.Rmd and .md) will not be uploaded to
the server.
launch.browser If true, the system’s default web browser will be launched automatically after
the app is started. Defaults to TRUE in interactive sessions only.
logLevel One of "quiet", "normal" or "verbose"; indicates how much logging to the
console is to be performed. At "quiet" reports no information; at "verbose",
a full diagnostic log is captured.
lint Lint the project before initiating deployment, to identify potentially problematic
code?
metadata Additional metadata fields to save with the deployment record. These fields will
be returned on subsequent calls to deployments().
python Full path to a python binary for use by reticulate. Required if reticulate
is a dependency of the app being deployed. The specified python binary will be
invoked to determine its version and to list the python packages installed in the
environment.
See Also
Other Deployment functions: applications, deployAPI, deployApp, deployDoc, deployTFModel
deployTFModel
Deploy a TensorFlow saved model

#### Description

Deploys a directory containing a Tensorflow saved model file.

#### Usage
<pre><code>

deployTFModel(modelDir, ...)

</code></pre>
#### Arguments

modelDir Path to the saved model directory. MUST contain saved_model.pb or saved_model.pbtxt
... Additional arguments to deployApp().forgetDeployment
17
Details
Deploy a single Tensorflow saved model as a bundle. Should be passed a directory that contains the
saved_model.pb or saved_model.pbtxt file, as well as any variables and assets necessary to load the
model.
A saved model directory might look like this:
./1/
./1/saved_model.pb or ./1/saved_model.pbtxt
./1/variables/
./1/variables/variables.data-00000-of-00001
./1/variables/variables.index
For information on creating saved models, see the Keras method keras::export_savedmodel.keras.engine.training.Mo
or the TensorFlow method tensorflow::export_savedmodel(). If using the TensorFlow package
for R, the official TensorFlow guide for saving and restoring models may be useful.
References
https://www.tensorflow.org/programmers_guide/saved_model#overview_of_saving_and_
restoring_models
#### See Also
Other Deployment functions: applications, deployAPI, deployApp, deployDoc, deploySite
forgetDeployment
Forget Application Deployment

#### Description

Forgets about an application deployment. This is useful if the application has been deleted on the
server, or the local deployment information needs to be reset.

#### Usage
<pre><code>

forgetDeployment(appPath = getwd(), name = NULL, account = NULL,
server = NULL, dryRun = FALSE, force = !interactive())

</code></pre>
#### Arguments

appPath The path to the content that was deployed, either a directory or an individual
document.
name The name of the content that was deployed (optional)
account The name of the account to which the content was deployed (optional)
server The name of the server to which the content was deployed (optional)18
generateAppName
dryRun Set to TRUE to preview the files/directories to be removed instead of actually
removing them. Defaults to FALSE.
force Set to TRUE to remove files and directories without prompting. Defaults to
FALSE in interactive sessions.
Details
This method removes from disk the file containing deployment metadata. If "name", "account", and
"server" are all NULL, then all of the deployments for the application are forgotten; otherwise, only
the specified deployment is forgotten.

#### Value
NULL, invisibly.


## generateAppName
Generate Application Name

#### Description

Generate a short name (identifier) for an application given an application title.

#### Usage
<pre><code>

generateAppName(appTitle, appPath = NULL, account = NULL,
unique = TRUE)

</code></pre>
#### Arguments

appTitle A descriptive title for the application.
appPath The path to the application’s content, either a directory or an individual docu-
ment. Optional.
account The account where the application will be deployed. Optional.
unique Whether to try to generate a unique name.
Details
This function modifies the title until it forms a suitable application name. Suitable application
names are 3 - 64 characters long and contain only alphanumeric characters.
The function is intended to be used to find a name for a new application. If appPath and account
are both specified, then the returned name will also be unique among locally known deployments
of the directory (note that it is not guaranteed to be unique on the server). This behavior can be
disabled by setting unique = FALSE.
Value
Returns a valid short name for the application.lint
19

#### Examples
```{r}

# Generate a short name for a sample application
generateAppName("My Father's Country", "~/fathers-country", "myacct")
lint
Lint a Project

#### Description

Takes the set of active linters (see addLinter()), and applies them to all files within a project.

#### Usage
<pre><code>

lint(project, files = NULL, appPrimaryDoc = NULL)

</code></pre>
#### Arguments

project Path to a project directory.
files Specific files to lint. Can be NULL, in which case all the files in the directory
will be linted.
appPrimaryDoc The primary file in the project directory. Can be NULL, in which case it’s in-
ferred (if possible) from the directory contents.

## ``linter``
Create a Linter

#### Description

Generate a linter, which can identify errors or problematic regions in a project.

#### Usage
<pre><code>

linter(apply, takes, message, suggestion)

</code></pre>
#### Arguments

apply Function that, given the content of a file, returns the indices at which problems
were found.
takes Function that, given a set of paths, returns the subset of paths that this linter
uses.
message Function that, given content and lines, returns an informative message for the
user. Typically generated with makeLinterMessage().
suggestion String giving a prescribed fix for the linted problem.20
listBundleFiles

#### Examples
```{r}

addLinter("no.capitals", linter(
## Identify lines containing capital letters -- either by name or by index
apply = function(content, ...) {
grep("[A-Z]", content)
},
## Only use this linter on R files (paths ending with .r or .R)
takes = function(paths) {
grep("[rR]$", paths)
},
# Use the default message constructor
message = function(content, lines, ...) {
makeLinterMessage("Capital letters found on the following lines", content, lines)
},
))
# Give a suggested prescription
suggest = "Do not use capital letters in these documents."
```

listBundleFiles
List Files to be Bundled

#### Description

Given a directory containing an application, returns the names of the files to be bundled in the
application.

#### Usage
<pre><code>

listBundleFiles(appDir)

</code></pre>
#### Arguments

appDir
Directory containing the application.
Details
This function computes results similar to a recursive directory listing from list.files(), with the
following constraints:
1. If the total size of the files exceeds the maximum bundle size, no more files are listed. The
maximum bundle size is controlled by the rsconnect.max.bundle.size option.
2. If the total size number of files exceeds the maximum number to be bundled, no more files are
listed. The maximum number of files in the bundle is controlled by the rsconnect.max.bundle.files
option.
3. Certain files and folders that don’t need to be bundled, such as those containing internal ver-
sion control and RStudio state, are excluded.makeLinterMessage
21
Value
Returns a list containing the following elements:
contents
totalSize
A list of the files to be bundled
The total size of the files



servers
Server Management Functions

#### Description

Functions to manage the list of known servers to which rsconnect can deploy and manage applica-
tions.

#### Usage
<pre><code>

servers(local = FALSE)
discoverServers(quiet = FALSE)
addConnectServer(url, name = NULL, certificate = NULL, quiet = FALSE)
addServer(url, name = NULL, certificate = NULL, quiet = FALSE)
removeServer(name)
serverInfo(name)
addServerCertificate(name, certificate, quiet = FALSE)

</code></pre>
#### Arguments

local Return only local servers (i.e. not shinyapps.io)
quiet Suppress output and prompts where possible.
url Server’s URL. Should look like http://servername/ or http://servername:port/.
name Optional nickname for the server. If none is given, the nickname is inferred from
the server’s hostname.
certificate Optional; a path a certificate file to be used when making SSL connections to
the server. The file’s contents are copied and stored by the rsconnect package.
Can also be a character vector containing the certificate’s contents.
Details
Register a server with addServer or discoverServers (the latter is useful only if your administra-
tor has configured server autodiscovery). Once a server is registered, you can connect to an account
on the server using connectUser().
The servers and serverInfo functions are provided for viewing previously registered servers.
There is always at least one server registered (the shinyapps.io server)28
setAccountInfo
Value
servers returns a data frame with registered server names and URLs. serverInfo returns a list
with details for a particular server.

#### Examples
```{r}

## Not run:
# register a local server
addServer("http://myrsconnect/", "myserver")
# list servers
servers(local = TRUE)
# connect to an account on the server
connectUser(server = "myserver")
## End(Not run)
```

setAccountInfo
Set ShinyApps Account Info

#### Description

Configure a ShinyApps account for publishing from this system.

#### Usage
<pre><code>

setAccountInfo(name, token, secret)

</code></pre>
#### Arguments

name Name of account to save or remove
token User token for the account
secret User secret for the account
See Also
Other Account functions: accounts, connectUser

#### Examples
```{r}

## Not run:
# register an account
setAccountInfo("user", "token", "secret")
# remove the same account
removeAccount("user")
## End(Not run)
```


showMetrics
Show Application Metrics

#### Description

Show application metrics of a currently deployed application

#### Usage
<pre><code>

showMetrics(metricSeries, metricNames, appDir = getwd(),
appName = NULL, account = NULL, server = NULL, from = NULL,
until = NULL, interval = NULL)

</code></pre>
#### Arguments

metricSeries Metric series to query. Refer to the shinyapps.io documentation for available
series.
metricNames Metric names in the series to query. Refer to the shinyapps.io documentation for
available metrics.
appDir * ``appDir``: Directory containing application. Defaults to current working directory.
appName Name of application
account Account name. If a single account is registered on the system then this parameter
can be omitted.
server Server name. Required only if you use the same account name on multiple
servers.
from Date range starting timestamp (Unix timestamp or relative time delta such as
"2d" or "3w").32
show
#### Usage
<pre><code>

until Date range ending timestamp (Unix timestamp or relative time delta such as
"2d" or "3w").
interval Summarization interval. Data points at intervals less then this will be grouped.
(Relative time delta e.g. "120s" or "1h" or "30d").
Note
This function only works for ShinyApps servers.
showProperties
Show Application property

#### Description

Show propreties of an application deployed to ShinyApps.

#### Usage
<pre><code>

showProperties(appPath = getwd(), appName = NULL, account = NULL)

</code></pre>
#### Arguments

appPath Directory or file that was deployed. Defaults to current working directory.
appName Name of application
account Account name. If a single account is registered on the system then this parameter
can be omitted.
Note
This function works only for ShinyApps servers.
show
#### Usage
<pre><code>

Show Application 
#### Usage
<pre><code>


#### Description

Show application usage of a currently deployed application

#### Usage
<pre><code>

show
#### Usage
<pre><code>
(appDir = getwd(), appName = NULL, account = NULL,
server = NULL, usageType = "hours", from = NULL, until = NULL,
interval = NULL)showUsers
33

</code></pre>
#### Arguments

appDir
appName
account
server
usageType
from
until
interval
* ``appDir``: Directory containing application. Defaults to current working directory.
Name of application
Account name. If a single account is registered on the system then this parameter
can be omitted.
Server name. Required only if you use the same account name on multiple
servers.
Use metric to retreive (for example: "hours")
Date range starting timestamp (Unix timestamp or relative time delta such as
"2d" or "3w").
Date range ending timestamp (Unix timestamp or relative time delta such as
"2d" or "3w").
Summarization interval. Data points at intervals less then this will be grouped.
(Relative time delta e.g. "120s" or "1h" or "30d").
Note
This function only works for ShinyApps servers.
showUsers
List authorized users for an application

#### Description

List authorized users for an application

#### Usage
<pre><code>

showUsers(appDir = getwd(), appName = NULL, account = NULL,
server = NULL)

</code></pre>
#### Arguments

appDir
appName
account
server
* ``appDir``: Directory containing application. Defaults to current working directory.
Name of application.
Account name. If a single account is registered on the system then this parameter
can be omitted.
Server name. Required only if you use the same account name on multiple
servers.
Note
This function works only for ShinyApps servers.
See Also
addAuthorizedUser() and showInvited()34
tasks
taskLog
Show task log

#### Description

Writes the task log for the given task

#### Usage
<pre><code>

taskLog(taskId, account = NULL, server = NULL, output = NULL)

</code></pre>
#### Arguments

taskId Task Id
account Account name. If a single account is registered on the system then this parameter
can be omitted.
server Server name. Required only if you use the same account name on multiple
servers (see servers())
output Where to write output. Valid values are NULL or stderr
See Also
tasks()

#### Examples
```{r}

## Not run:
# write task log to stdout
taskLog(12345)
# write task log to stderr
taskLog(12345, output="stderr")
## End(Not run)
```

tasks

#### Description

List Tasks
List TasksterminateApp
35

#### Usage
<pre><code>

tasks(account = NULL, server = NULL)

</code></pre>
#### Arguments

account Account name. If a single account is registered on the system then this parameter
can be omitted.
server Server name. Required only if you use the same account name on multiple
servers (see servers())
Value
Returns a data frame with the following columns:
id
action
status
created_time
finished_time
Task id
Task action
Current task status
Task creation time
Task finished time
See Also
taskLog()

#### Examples
```{r}

## Not run:
# list tasks for the default account
tasks()
## End(Not run)
```

terminateApp
Terminate an Application

#### Description

Terminate and archive a currently deployed ShinyApps application.

#### Usage
<pre><code>

terminateApp(appName, account = NULL, server = NULL, quiet = FALSE)36
unsetProperty

</code></pre>
#### Arguments

appName Name of application to terminate
account Account name. If a single account is registered on the system then this parameter
can be omitted.
server Server name. Required only if you use the same account name on multiple
servers (see servers())
quiet Request that no status information be printed to the console during the termina-
tion.
Note
This function only works for ShinyApps servers.
See Also
applications(), deployApp(), and restartApp()

#### Examples
```{r}

## Not run:
# terminate an application
terminateApp("myapp")
## End(Not run)
unsetProperty
Unset Application property

#### Description

Unset a property on currently deployed ShinyApps application (restoring to its default value)

#### Usage
<pre><code>

unsetProperty(propertyName, appPath = getwd(), appName = NULL,
account = NULL, force = FALSE)

</code></pre>
#### Arguments

propertyName Name of property to unset
appPath Directory or file that was deployed. Defaults to current working directory.
appName Name of application
account Account name. If a single account is registered on the system then this parameter
can be omitted.
force Forcibly unset the propertywriteManifest
37
Note
This function only works for ShinyApps servers.

#### Examples
```{r}

## Not run:
# unset application package cache property to revert to default
unsetProperty("application.package.cache")
## End(Not run)
```
writeManifest
Create a manifest.json describing deployment requirements.

#### Description

Given a directory content targeted for deployment, write a manifest.json into that directory describing the deployment requirements for that content.

#### Usage
<pre><code>

writeManifest(appDir = getwd(), appFiles = NULL,
appPrimaryDoc = NULL, contentCategory = NULL, python = NULL)

</code></pre>
#### Arguments

appDir Directory containing the content (Shiny application, R Markdown document, etc).
appFiles Optional. The full set of files and directories to be included in future deployments of this content. Used when computing dependency requirements. When
NULL, all files in appDir are considered.
appPrimaryDoc Optional. Specifies the primary document in a content directory containing more than one. If NULL, the primary document is inferred from the file list.
contentCategory
python
Optional. Specifies the kind of content being deployed (e.g. "plot" or "site").
Full path to a python binary for use by reticulate. The specified python binary will be invoked to determine its version and to list the python packages installed
in the environment.