---
title: "``rsconnect::appDependencies``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rsconnect)
```
Detect Application Dependencies

#### Description

Recursively detect all package dependencies for an application. This function parses all .R files in the application directory to determine what packages the application depends on; and for each of those packages what other packages they depend on.

#### Usage
<pre><code>

appDependencies(appDir = getwd(), appFiles = NULL)

</code></pre>
#### Arguments

* ``appDir``: Directory containing application. Defaults to current working directory.
* ``appFiles``:  The files and directories and deploy (only if upload = TRUE). Can be NULL, in which case all the files in the directory containing the application are bundled. Takes precedence over appFileManifest if both are supplied.




#### Examples
```{r}

# dependencies for the app in the current working dir
appDependencies()

# dependencies for an app in another directory
appDependencies("~/projects/shiny/app1")

```

#### Details
Dependencies are determined by parsing application source code and looking for calls to library,
require, ::, and :::.
Recursive dependencies are detected by examining the Depends, Imports, and ``LinkingTo`` fields of the packages immediately dependend on by the application.

#### Value
Returns a data frame listing the package dependencies detected for the application:
package
version
Name of package
Version of package

#### Note
Since the Suggests field is not included when determining recursive dependencies of packages, it’s possible that not every package required to run your application will be detected.
In this case, you can force a package to be included dependency by inserting call(s) to require within your source directory. This code need not actually execute, for example you could create a standalone file named dependencies.R with the following code:

<pre><code>
require(xts)
require(colorspace)
</code></pre>
This will force the xts and colorspace packages to be installed along with the rest of your appli-
cation when it is deployed.
See Also
rsconnectPackages(Using Packages with rsconnect)
