---
title: "``rsconnect::applications``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rsconnect)
```


List Deployed Applications

#### Description

List all applications currently deployed for a given account.

#### Usage
<pre><code>

applications(account = NULL, server = NULL)

</code></pre>
#### Arguments

* account Account name. If a single account is registered on the system then this parameter can be omitted.
* server Server name. Required only if you use the same account name on multiple servers.

#### Value
Returns a data frame with the following columns:

name
url
config_url
status

Name of application
URL where application can be accessed
URL where application can be configured
Current status of application. Valid values are pending, deploying, running, terminating, and terminated.

#### Note
To register an account you call the setAccountInfo() function.
See Also
deployApp(), terminateApp()
Other Deployment functions: deployAPI, deployApp, deployDoc, deploySite, deployTFModel

#### Examples
```{r}

## Not run:
# list all applications for the default account
applications()
# list all applications for a specific account
applications("myaccount")
# view the list of applications in the data viewer
View(applications())
## End(Not run)

```
