---
title: "``rsconnect::rpubsUpload()``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

rpubsUpload
23
Upload a file to RPubs

#### Description

This function publishes a file to rpubs.com. If the upload succeeds a list that includes an id and continueUrl is returned. A browser should be opened to the continueUrl to complete publishing of the document. If an error occurs then a diagnostic message is returned in the error element of the list.

#### Usage
<pre><code>

rpubsUpload(title, contentFile, originalDoc, id = NULL,
properties = list())

</code></pre>
#### Arguments

* title The title of the document.
* contentFile The path to the content file to upload.
* originalDoc The document that was rendered to produce the contentFile. May be NULL if the document is not known.
* id If this upload is an update of an existing document then the id parameter should specify the document id to update. Note that the id is provided as an element of
the list returned by successful calls to rpubsUpload.
* properties A named list containing additional document properties (RPubs doesn’t currently expect any additional properties, this parameter is reserved for future use).
* Value A named list. If the upload was successful then the list contains a id element that can be used to subsequently update the document as well as a continueUrl element that provides a URL that a browser should be opened to in order to complete publishing of the document. If the upload fails then the list contains an error element which contains an explanation of the error that occurred.

#### Examples
```{r}

## Not run:
# upload a document
result <- rpubsUpload("My document title", "Document.html")
if (!is.null(result$continueUrl))
browseURL(result$continueUrl)
else
stop(result$error)
# update the same document with a new title
updateResult <- rpubsUpload("My updated title", "Document.html",
id = result$id)24
rsconnectOptions
## End(Not run)
```