---
title: "``rsconnect::setProperty``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rsconnect)
```

setProperty
Set Application property

#### Description

Set a property on currently deployed ShinyApps application.

#### Usage
<pre><code>

setProperty(propertyName, propertyValue, appPath = getwd(),
appName = NULL, account = NULL, force = FALSE)

</code></pre>
#### Arguments

propertyName Name of property to set
propertyValue Nalue to set property to
appPath Directory or file that was deployed. Defaults to current working directory.
appName Name of application
account Account name. If a single account is registered on the system then this parameter
can be omitted.
force Forcibly set the property
Note
This function only works for ShinyApps servers.

#### Examples
```{r}

## Not run:
# set instance size for an application
setProperty("application.instances.count", 1)
# disable application package cache
setProperty("application.package.cache", FALSE)
## End(Not run)30
showLogs
